### 2014-02-28 poster/paper.tex
poster fixes

  %\documentclass[final,hyperref={pdfpagelabels=false}]{beamer} % beamer 3.07: get rid of beamer warnings
  \mode<presentation> {  %% check http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php for examples
    \usetheme{Berlin}    %% you should define your own theme e.g. for big headlines using your own logos 
  }
\setbeamercolor{block body}{bg=white, fg=black}
\setbeamerfont{block title}{size=\Large}
  \usepackage[english]{babel}
  \usepackage[latin1]{inputenc}
  \usepackage{amsmath,amsthm, amssymb, latexsym}
  \usepackage{float}
\usepackage{color}
\usepackage{pgfplots}
\usepackage{anyfontsize}
  %\usepackage{times}\usefonttheme{professionalfonts}  % times is obsolete
  \usefonttheme[onlymath]{serif}
  \boldmath
  \usepackage[orientation=portrait,size=a0,scale=1.2, debug]{beamerposter}                       % e.g. for DIN-A0 poster
  %\usepackage[orientation=portrait,size=a1,scale=1.4,grid,debug]{beamerposter}                  % e.g. for DIN-A1 poster, with optional grid and debug output
  %\usepackage[size=custom,width=200,height=120,scale=2,debug]{beamerposter}                     % e.g. for custom size poster
  %\usepackage[orientation=portrait,size=a0,scale=1.0,printer=rwth-glossy-uv.df]{beamerposter}   % e.g. for DIN-A0 poster with rwth-glossy-uv printer check
  % ...
\definecolor{OliveGreen}{HTML}{eeeeee}

@@

		\begin{block}{Current Hadoop File System Architecture}
			\includegraphics[scale=1]{assets/hadoop_architecture.pdf}
		\end{block}

	  \begin{block}{Panthera Architecture}
		\includegraphics[scale=1]{assets/panthera_architecture_complete.pdf}	  
	  \end{block}

	  \begin{block}{Panthera Metadata Architecture}
	  \includegraphics[scale=1]{assets/panthera_metadata.pdf}
      \end{block}

      \begin{block}{Panthera Data Architecture}
      \includegraphics[scale=1]{assets/panthera_architecture.pdf}
      \end{block}

@@

@@

	\begin{block}{Results}
		\includegraphics[scale=1.2]{assets/box-plot-data.pdf}
		\vspace{1em}
		\includegraphics[scale=1.2]{assets/box-plot-metadata.pdf}
		\vspace{1em}
		\includegraphics[scale=1.2]{assets/box-plot-meta-multinode.pdf}
	\end{block}

>>>>

  %\documentclass[final,hyperref={pdfpagelabels=false}]{beamer} % beamer 3.07: get rid of beamer warnings
  \mode<presentation> {  %% check http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php for examples
    \usetheme{Berlin}    %% you should define your own theme e.g. for big headlines using your own logos 
  }
\setbeamercolor{block body}{bg=white, fg=black}
\setbeamerfont{block title}{size=\Large}
  \usepackage[english]{babel}
  \usepackage[latin1]{inputenc}
  \usepackage{amsmath,amsthm, amssymb, latexsym}
  \usepackage{float}
\usepackage{color}
\usepackage{pgfplots}
\usepackage{anyfontsize}
  %\usepackage{times}\usefonttheme{professionalfonts}  % times is obsolete
  \usefonttheme[onlymath]{serif}
  \boldmath
  \usepackage[orientation=portrait,size=a0,scale=1.15, debug]{beamerposter}                       % e.g. for DIN-A0 poster
  %\usepackage[orientation=portrait,size=a1,scale=1.4,grid,debug]{beamerposter}                  % e.g. for DIN-A1 poster, with optional grid and debug output
  %\usepackage[size=custom,width=200,height=120,scale=2,debug]{beamerposter}                     % e.g. for custom size poster
  %\usepackage[orientation=portrait,size=a0,scale=1.0,printer=rwth-glossy-uv.df]{beamerposter}   % e.g. for DIN-A0 poster with rwth-glossy-uv printer check
  % ...
\definecolor{OliveGreen}{HTML}{eeeeee}

@@

		\begin{block}{Current Hadoop File System Architecture}
			\centerline{\includegraphics[scale=1.5]{assets/vanilla_hadoop.pdf}}
		\end{block}

	  \begin{block}{Panthera Architecture}
		\centerline{\includegraphics[scale=1.5]{assets/panthera_architecture_complete_larger.pdf}}	  
	  \end{block}

		\begin{block}{Panthera Metadata Architecture}
	 		\centerline{\includegraphics[scale=1.5]{assets/panthera_metadata_large.pdf}}
      	\end{block}

@@

      \begin{block}{Panthera Data Architecture}
      \includegraphics[scale=1.2]{assets/panthera_data_large.pdf}
     \end{block}

@@

	\begin{block}{Results}
		\includegraphics[scale=1.10]{assets/box-plot-data-larger.pdf}
		\vspace{1em}
		\includegraphics[scale=1.1]{assets/box-plot-metadata-larger.pdf}
		\vspace{1em}
		\includegraphics[scale=1.1]{assets/box-plot-meta-multinode-larger.pdf}
	\end{block}
